Details of specific functions

### 2019-07-24 inst/gitbook/03_specific-tutorials.Rmd
man pre-update
Updated span.tree.length

## Time slicing

@@

## Customised subsets

@@

\begin{equation}
    span.tree.length = \sum(\mathrm{branch\ length})
\end{equation}

@@

#### Centroids, displacements, and ancestral distance metrics

@@

```{r}
## The length of the minimal spanning tree
summary(dispRity(dummy_space, metric = span.tree.length))
```

>>>>

## Time slicing {#chrono-subsets}

@@

## Customised subsets {#custom-subsets}

@@

\begin{equation}
    span.tree.length = \mathrm{branch\ length}
\end{equation}

@@

#### Centroids, displacements, and ancestral distance metrics {#centroids}

@@

```{r}
## The length of the minimal spanning tree
summary(dispRity(dummy_space, metric = c(sum, span.tree.length)))
```
